Supplement to: Learning to Infer Graphics Programs from Hand-Drawn Images

### 2017-07-26 synthesizerOutputs.tex
updated the supplement to have the latest parsing results

            \begin{tabular}{lll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-71.png}&
            Sampled no finished traces.&

@@

            \begin{tabular}{lll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-73.png}&
            Sampled no finished traces.&

@@

            \begin{tabular}{lll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-94.png}&
            Sampled no finished traces.&

>>>>

            \begin{tabular}{lll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-71.png}&
            \includegraphics[width = 5cm]{../TikZ/drawings/expert-71-parses/0.png}&

@@

            \begin{tabular}{lll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-73.png}&
            \includegraphics[width = 5cm]{../TikZ/drawings/expert-73-parses/0.png}&

@@

            \begin{tabular}{lll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-94.png}&
            \includegraphics[width = 5cm]{../TikZ/drawings/expert-94-parses/0.png}&
